---
title: "W_UP_01"
author: "Andrew Valles Tovar"
date: "Spring 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Plot boxplots

```{r}
boxplot(pushups~position,data=mydata)
```
  
Skill players do more push ups than Line players. You're able to determine why skill players do more push ups than the line layers is because the SKILL box has a higher position on the plot than the LINE box.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(pushups~position,data=mydata)
```
  
On the average, skill players do about 3 times more push ups than the line players. You can see that through the mean category.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```
The probability of getting a result like this is 0.000009421 if there really is no difference between line and skill doing push ups. I reject the hypothesis that line players are able to catch up in push ups compared to skill players due to the huge gap between the two with skill players in the lead.
  
# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
Using box plots, numerical descriptive results, and inferential results, we were able to determine that skill players do significantly more push ups than line players. For box plots, we used the graph to see that the box labelled "SKILL" was placed at a higher position than the "LINE" box. In numerical descriptive results, skill players did three times more average push ups than line players. Finally, the probability of there being no difference between line and skill players doing push ups was extremely low, so the conclusion was the hypothesis was completely absurd. Therefore, the ultimate result is that skill players do more push ups than line players.
